\textsf{\textbf{Analyzing \textit{Streptococcus mutans} RNA-Seq data using R packages}}

### 2012-01-06 package/smutans/inst/doc/smutans.Rnw
Just an update.

\begin{abstract}
We analyze a number of RNA samples from \textit{Streptococcus mutans} using R
packages: \Rpackage{DESeq}, \Rpackage{edgeR}, and \Rpackage{goseq}.
Tasks include the analysis of count data from RNA-Seq for
the detection of differentially expressed genes.  Tests of enrichment for
differentially expressed genes are performed using \Rpackage{goseq}.  The
package \Rpackage{smutans} contains the procedures.  This vignette explains the
use of the package. 
\end{abstract}

@@

We can create \Rclass{CountDataSet} objects using functions that are not
exported. One should create an R script at the directory that contains the
source code of the \Rpackage{smutans}. Put the following scripts in the R script
and run the script at the directory. That should create RData files at
the directory smutans/data: sm835Genes.RData, smutansGenes.RData.
<<samplePreparation,eval=FALSE>>=
#not run
library(DESeq)
source("smutans/R/core.R")
smutans.prepareData835NPP( )
smutans.prepareDataUA159TW1( ) 
smutans.prepareGoseq( )
q("no")
@

@@

>>>>

\begin{abstract}
We analyze a number of RNA samples from \textit{Streptococcus mutans} using R
packages: \Rpackage{DESeq}, \Rpackage{edgeR}, and \Rpackage{goseq}.
Tasks include the analysis of count data from RNA-Seq for
the detection of differentially expressed genes, and tests of enrichment for
differentially expressed genes using \Rpackage{goseq}.  The
package \Rpackage{smutans} contains procedures that make use of functions
provided by the above R packages.  
\end{abstract}

@@

We can create \Rclass{CountDataSet} objects using functions that are not
exported. One should create an R script at the directory that contains the
source code of the \Rpackage{smutans}. Put the following scripts in the R script
and run the script at the directory. That should create RData files at
the directory smutans/data: sm835Genes.RData, smutansGenes.RData.

http://www.oralgen.lanl.gov/oralgen/downloads/smut.csv

http://www.oralgen.lanl.gov/cgi-bin/gene_id_search.cgi?dbname=smut&gene_id=SMu0001

\fixme{Where are flat files for genes of S. mutans UA159?}

<<samplePreparation,eval=FALSE>>=
#not run
library(DESeq)
source("smutans/R/core.R")
smutans.prepareData34( )
smutans.prepareData835NPP( )
smutans.prepareDataUA159TW1( ) 
smutans.prepareGoseq( )
q("no")
@

@@

\fixme{OMZ175, UA159CSP, SMU86CSP pairwise comparisons should be done fairly
easily after detailed analyses.}
